Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-17 papers/EMNLP2019/analysis.tex

\begin{figure*}
\begin{minipage}[b]{0.4\linewidth}
\includegraphics[scale=.4]{Figures/types_instances.png}
\end{minipage}
\begin{minipage}[b]{0.6\linewidth}
\includegraphics[scale=.4]{Figures/types_classes.png}
\end{minipage}
 \caption{\label{fig:ntypes} Cumulative histograms for number of types found for instances and classes, based on different frequency tresholds (applied on the level of instances and classes respectively)}
\end{figure*}

@@

\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2379889_1353176_supercat_unique.png}}  sandwich (15), basket (6), food (5), burger (2), hamburger (2), meal (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394266_465678_singleton_obj.png}} food (10), sandwich (8), toast (5), french toast (4), dessert (2), breakfast (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), food (7), bun (4), sandwich (3), bread (2)\\ 

@@

\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1592509_1610006_singleton_obj.png}} bridge (20), building (11)  &

@@

\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), person (3), baseball player (2) &
  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), baseball player (7), batter (5), player (3), helmet (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), baseball player (4), player (4), man (3), child (3), batter (3), dress (2), kid (2)&
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), player (5), shoe (4), bat (4), person (4), legs (4), baseball player (3), hitter (2)\\ 

@@

\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), bathrobe (5) &

@@

\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), sweater (9), coat (3), doll (3), toy (3), shirt (2), bear (2), robe (2)\\

@@

 \caption{\label{fig:ex}Examples for different instances of VG synsets with low and high agreement in MN data set}
\end{figure*}

>>>>

\begin{figure*}
\begin{minipage}[b]{0.4\linewidth}
\includegraphics[scale=.4]{figures/types_instances.png}
\end{minipage}
\begin{minipage}[b]{0.6\linewidth}
\includegraphics[scale=.4]{figures/types_classes.png}
\end{minipage}
 \caption{\label{fig:ntypes} Cumulative histograms for number of types found for instances and classes, based on different frequency tresholds (applied on the level of instances and classes respectively)}
\end{figure*}

@@

\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2379889_1353176_supercat_unique.png}}  sandwich (15), basket (6), \underline{food} (5), burger (2),  \underline{hamburger} (2),  \underline{meal} (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394266_465678_singleton_obj.png}} \underline{food} (10), sandwich (8), toast (5), french toast (4), dessert (2), breakfast (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), \underline{food} (7), bun (4), sandwich (3),  \underline{bread} (2)\\ 

@@

\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1592509_1610006_singleton_obj.png}} bridge (20),  \underline{building} (11)  &

@@

\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), \underline{person} (3), \underline{baseball player} (2) &
  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), \underline{baseball player} (7), batter (5), \underline{player} (3), helmet (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), \underline{baseball player} (4), \underline{player} (4), man (3), child (3), batter (3), dress (2), kid (2)&
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), \underline{player} (5), shoe (4), bat (4), \underline{person} (4), legs (4), \underline{baseball player} (3), hitter (2)\\ 

@@

\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), \underline{bathrobe} (5) &

@@

\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), \underline{sweater} (9), coat (3), doll (3), toy (3), \underline{shirt} (2), bear (2), robe (2)\\

@@

 \caption{\label{fig:ex}Examples for different instances of VG synsets with low and high agreement in MN data set, names that have a hierarchical relation to the VG synset in WordNet are underlined}
\end{figure*}
